%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Prerequisites}

\begin{frame}{Python version}

    \begin{block}{Python 2 or 3?}
    "Python 2.x is legacy, Python 3.x is the present and future of the language" from www.python.org/doc 
    \end{block}

    \begin{block}{PIRS uses Python 2.x}
    PIRS is developed for Python 2.6.x or above. Not for Python 3.x!
    \end{block}
                
    Usually Python 2.6.x or 2.7.x is already installed. If not, can be
    installed using OS installer (e.g. Ubuntu Software Center), or compiled
    from sources.

\end{frame}

\begin{frame}[fragile]
    \frametitle{Required packages}
    \begin{block}{uncertainties} 
        Needed to preserve information about errors in MC calculations. 

        \begin{bashcode*}{gobble=12}
            $ wget https://pypi.python.org/.../uncertainties-2.4.6.tar.gz
            $ tar -xzf uncertainties-2.4.6.tar.gz
            $ cd uncertainties-2.4.6
            $ python setup.py install --user
        \end{bashcode*}
    \end{block}

    \begin{block}{matplotlib}
        Optional. Needed to plot geometry and results of calculations. 
        
        Simplest way to install -- using OS installer. Compilation from sources
        is difficult due to lot of dependencies.
    \end{block}

\end{frame}

\begin{frame}[fragile]
    \frametitle{Environmental variables}
    Several enviromental variables should be defined.

    \begin{block}{\$DATAPATH}
        Path to xsdir file and files with cross-sections.

        \begin{bashcode}
            $ echo $DATAPATH
            /home/data/mcnp
        \end{bashcode}
    \end{block}

    \begin{block}{\$MCNP}
        Path to MCNP executable

        \begin{bashcode}
            $ echo $MCNP
            /home/bin/mcnp5_linux_i386_omp
        \end{bashcode}
    \end{block}

    \begin{block}{\$SCF}
        Path to SCF executable

        \begin{bashcode}
            $ echo $SCF
            /home/bin/scf25_intel
        \end{bashcode}
    \end{block}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PIRS installation}

\begin{frame}[fragile]
    \frametitle{How to install PIRS}
    
    \begin{block}{Standard method}
        \begin{bashcode}
            $ tar -xzf pirs-0.2a.0.tar.gz
            $ cd pirs-0.2a.0
            $ python setup.py install --user
        \end{bashcode}

        Dependencies should be installed separately.
    \end{block}


    \begin{block}{2-nd method}
        It uses pip -- python package installer that is not available by default.

        \begin{bashcode}
            $ pip install pirs-0.2a.0.tar.gz --user
        \end{bashcode}

        Dependencies will be installed by pip, if necessary.
    \end{block}

    \begin{block}{Test}
        \begin{pythoncode}
            from pirs.solids import Box
            from pirs import McnpInterface
            b = Box()
            m = McnpInterface(b)
            m.run('r')
        \end{pythoncode}
    \end{block}

\end{frame}



